Argennon: A Scalable Smart Contract Platform

### 2022-04-14 tex/A.tex
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the commitment scheme is kept manageable.
    \end{abstract}
    \tableofcontents

>>>>

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the commitment scheme is kept manageable.

        The Argennon network relies on a permission-less network of Publicly Verifiable Database (PV-DB) servers,
        which forms the Argennon cloud. A PV-DB server is a conventional data server which uses its computational and
        storage resources to help the
        Argennon network process transactions. A large portion of incentive rewards in the Argennon platform is
        devoted to PV-DB servers. This will incentivize the development of conventional networking, storage and
        computational hardware, which can benefit all areas of information technology.
    \end{abstract}
    \tableofcontents

### 2022-04-14 tex/sections/avm.tex
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}} Smart Contract Execution
Environment (AscEE) is an abstract execution environment for executing Argennon smarts contracts (a.k.a\ applications).
An Argennon application essentially is an HTTP server whose state is kept in the Argennon blockchain and
its logic is described using an Argennon Standard Representation (ASR).

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and requirements of the Argennon platform.
Argennon supports two standard representations: one is a high level text based language which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of applications logic to facilitate
platform specific compiler optimization at host nodes. On the other hand, the low level language is designed for
efficient direct execution of applications that are not frequently used.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data structures for executing requests are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} and in
the final step, requests are executed using this data structure.

>>>>

The Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}} Smart Contract Execution
Environment (AscEE) is an abstract execution environment for executing Argennon smarts contracts (a.k.a\ Argennon
applications). An Argennon application essentially is an HTTP server whose state is kept in the Argennon blockchain and
its logic is described using an Argennon Standard Representation (ASR).

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and requirements of the Argennon platform.
Argennon supports two standard representations: one is a high level text based language which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of applications logic to facilitate
platform specific compiler optimization at host nodes. The low level language, is designed for
efficient direct execution of applications that are not frequently used.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud and the helper data structures are constructed.
This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, requests are executed using that data structure.
